### 2018-03-10 paper/4-build.tex
Clean up build a bit

\todo{AM}{Turn the above into a formal definition of `correctness' and add a section that provides a mathematical definition of correctness, which does not rely on materialising intermediate values.}

@@

The topological approach creates a linear ordering, which when followed, ensures each build is correct. Given a function from a key to its dependencies, and an initial key, you can compute the linear ordering by first taking the transitive closure, then doing a topological sort. However, to go from a \hs{Compute} to the dependencies, it must be the case that it is Applicative.

\todo{NM}{In this case we can give actual code, so let's do that?}

@@

\subsubsection{Recording predicate trace}

An alternative way to determine if a key is dirty is to record what state the values/hashes of dependencies were used at last time, and if something has changed, the key is dirty and must be recomputed. For a monadic build system the trace can include what dependencies were used as well, although for an applicative system that information can be inferred. For each key, a single trace is recorded, so it naturally fits that the data is stored in an associative map indexed by target key.

@@

\subsubsection{Recording generative traces}

A predicate trace allows us to mark the key dirty and rebuild it, extending that we can store a \textit{generative} trace which is the trace plus the complete result. Once we are storing the complete result it makes sense to record many generative traces per key, and to share them with other users, providing cloud-build functionality.

\todo{NM}{I found terms `predicate' and `generative' hard to grasp and a bit abstract. Especially `predicate'. Let's replace it with `verifying'? And maybe `generative' with `recreating' since it allows to recreate values which were previously created by compute?}

\todo{NM}{I would also like to see an actual \hs{upToDate} function for verifying, and a \hs{recreate} for `recreating'.}

>>>>

@@

The topological approach creates a linear ordering, which when followed, ensures each build is correct. Given a function from a key to its dependencies, and an initial key, you can compute the linear ordering by first taking the transitive closure, then doing a topological sort. However, to go from a \hs{Compute} to the dependencies, it must be the case that the constraint is \hs{Applicative}, as per \S\ref{getdependencies}.

@@

\subsubsection{Verifying traces}

An alternative way to determine if a key is dirty is to record what state the values/hashes of dependencies were used at last time, and if something has changed, the key is dirty and must be recomputed - in essence a trace with which we can use to \textit{verify} existing values. For a monadic build system the trace can include what dependencies were used as well, although for an applicative system that information can be inferred. For each key, a single trace is recorded, so it naturally fits that the data is stored in an associative map indexed by target key.

@@

\subsubsection{Constructive traces}

A verifying trace allows us to mark the key dirty and rebuild it, extending that we can store a \textit{constructive} trace which is the trace plus the complete result. Once we are storing the complete result it makes sense to record many constructive traces per key, and to share them with other users, providing cloud-build functionality.

\todo{AM}{AM: I would also like to see an actual \hs{upToDate} function for verifying, and a \hs{recreate} for `recreating'. NM: }
